\texttt{bayesim}: a tool for fast model fitting with Bayesian inference

### 2018-08-30 paper/Manuscript.tex
cleaning docs, some paper updates

\begin{abstract}
Target journal: Computer Physics Communications
\end{abstract}

@@

 \begin{figure}
   \includegraphics[width=0.7\columnwidth]{figure_1.png}
   \caption{(Figure copied from docs website for now, will make a publication-appropriate version)}
   \label{fig1}
 \end{figure}

@@

  \begin{figure}
    \includegraphics[width=0.55\columnwidth]{structure.png}
    \includegraphics[width=0.4\columnwidth]{flowchart.png}
    \caption{Left: \texttt{bayesim} software structure, indicating class definitions, internal and external dependencies, and interfaces. Right: Flowchart of use of \texttt{bayesim}. (I will update these to make a more sensible figure with less white space, and also add subdivision into the loop)}
    \label{structure}
  \end{figure}

@@

    \begin{figure}
      \includegraphics[width=0.45\columnwidth]{diode_obs.png}
      \includegraphics[width=0.45\columnwidth]{diode_obs_zoom.png}
      \includegraphics[width=0.3\columnwidth]{diode_pmf_1.png}
      \includegraphics[width=0.65\columnwidth]{diode_comp_1.png}
      \includegraphics[width=0.3\columnwidth]{diode_pmf_2.png}
      \includegraphics[width=0.65\columnwidth]{diode_comp_2.png}
      \includegraphics[width=0.3\columnwidth]{diode_pmf_3.png}
      \includegraphics[width=0.65\columnwidth]{diode_comp_3.png}
      \caption{a) ``Observations" generated by ideal diode model, Equation~\ref{ID_eqn}, b) Observed data saved by \texttt{bayesim}, with zoom to show where neglected data points were, Next three rows: PMF's, comparisons of highest three probability model points with observed data, and absolute errors thereof, on the initial grid, and after one and two subdivisions, respectively. ``True'' values for the parameters indicated on the PMF in red. (this figure is a giant data dump right now; I'm figuring out how to make it less terrifyingly overwhelming - like possibly overlaying all three PMF's onto one plot in different colors)}
      \label{ID_data}
    \end{figure}

@@

    The next three rows of ~\autoref{ID_data} show the posterior distributions, comparison of JV data between observations and the three highest-probability model points, and absolute errors thereof, on the initial grid and after one and two rounds of subdivision. Note that the ranges on the parameter values get narrower as does the scale of absolute errors.

  \subsection{SnS Solar Cell}
    \begin{itemize}
      \item more practical example - replicating fit from Joule paper
      \item figure 4 showing PMF and comparison of JV curves
    \end{itemize}

>>>>

\begin{abstract}
  \hl{abstract text here}

  Target journal: Computer Physics Communications
\end{abstract}

@@

 \begin{figure}
   \includegraphics[width=0.7\columnwidth]{figure_1.png}
   \caption{\hl{(Figure copied from docs website for now, will make a publication-appropriate version)}}
   \label{fig1}
 \end{figure}

@@

  \begin{figure}
    \includegraphics[width=0.55\columnwidth]{structure.png}
    \includegraphics[width=0.4\columnwidth]{flowchart.png}
    \caption{Left: \texttt{bayesim} software structure, indicating class definitions, internal and external dependencies, and interfaces. Right: Flowchart of use of \texttt{bayesim}. \hl{(I will update these to make a more sensible figure with less white space, and also add subdivision into the loop)}}
    \label{structure}
  \end{figure}

@@

    \begin{figure}
      \includegraphics[width=0.33\columnwidth]{diode_obs.png}
      \includegraphics[width=0.45\columnwidth]{diode_obs_zoom.png}
%      \includegraphics[width=0.3\columnwidth]{diode_pmf_1.png}
%      \includegraphics[width=0.65\columnwidth]{diode_comp_1.png}
%      \includegraphics[width=0.3\columnwidth]{diode_pmf_2.png}
%      \includegraphics[width=0.65\columnwidth]{diode_comp_2.png}
%      \includegraphics[width=0.3\columnwidth]{diode_pmf_3.png}
%      \includegraphics[width=0.65\columnwidth]{diode_comp_3.png}
%      \caption{a) ``Observations" generated by ideal diode model, Equation~\ref{ID_eqn}, b) Observed data saved by \texttt{bayesim}, with zoom to show where neglected data points were, Next three rows: PMF's, comparisons of highest three probability model points with observed data, and absolute errors thereof, on the initial grid, and after one and two subdivisions, respectively. ``True'' values for the parameters indicated on the PMF in red. (this figure is a giant data dump right now; I'm figuring out how to make it less terrifyingly overwhelming - like possibly overlaying all three PMF's onto one plot in different colors)}
      \includegraphics[width=0.8\columnwidth]{all_PMFs.png}
      \caption{a) ``Observations" generated by ideal diode model, Equation~\ref{ID_eqn}, b) Observed data saved by \texttt{bayesim}, with zoom to show where neglected data points were, c) PMF's after the first inference run, second (one subdivision), and third (two subdivision), in blue, orange, and green, respectively. Values used to generate data indicated in red. \hl{(PMF figure will have a legend and I will add error plots, also observation data could be presented better too)}}
      \label{ID_data}
    \end{figure}

@@

    %The next three rows of ~\autoref{ID_data} show the posterior distributions, comparison of JV data between observations and the three highest-probability model points, and absolute errors thereof, on the initial grid and after one and two rounds of subdivision. Note that the ranges on the parameter values get narrower as does the scale of absolute errors.

    The lower part of ~\autoref{ID_data} shows the posterior distributions after the first inference run and after each round of subdivision, demonstrating that \texttt{bayesim} gets progressively closer to the ``true" values as the loop continues iterating. In addition, on the first inference run (prior to any subdivision), an average of 46\% of grid points had larger model uncertainty than experimental uncertainty, while after the second subdivision, only 2\% did.

  \subsection{SnS Solar Cell}
    This example aims to demonstrate a more realistic application of \texttt{bayesim}, i.e. when the model being used to compute likelihoods is more computationally expensive. In this case, we will repeat the analysis from Ref.~\cite{SnSJoule}, using SCAPS~\cite{SCAPS} as the model, which takes 10-15 core-seconds for a single J-V sweep.

    We start on significantly coarser grid than Ref.~\cite{SnSJoule} and will show one level of subdivision.
